```{css echo=FALSE}
.plateTable, .plateTable th, .plateTable td {
  border: 1px solid black;
}

.plateTable {border-collapse: collapse}

.plateWell.NSB{color:purple}
.plateWell.STD{color:blue}
.plateWell.QC{color:green}
.plateWell.bufferCtrl{color:red}
.plateWell.sample{color:black}

.plateTable tr:nth-child(4n + 3) td,
.plateTable tr:nth-child(4n + 4) td {
    background-color: #E8E8E8;
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
# options(digits=3)
```


```{r include=FALSE}
if(tinytex::is_tinytex() == FALSE){
  print("Instaling tinytex for pdf documents")
  tinytex::install_tinytex()
}
doc.type <- input$format
```

# Results
```{r}
meanSampleResults()%>%
  mutate(
    across(
      c(
        "cort",
        "cortCV"
      ),
      ~ round(.x, 3)
    )
  )
```

# The Plate 
```{r}
view_plate(
    assayPlate(),
    well_ids_column = "wells",
    columns_to_display = c("plateID")
  )[[1]]
```


# Buffer Control

The mean net OD for buffer control wells was `r bufferCtrlOD()`

```{r echo=FALSE}
assayPlate()%>%
  filter(
    type == "bufferCtrl"
  ) %>%
  select(
    wells, plateID, netOD
  )
```

# Percent Binding

This is the percent binding of each well relative to the buffer control mean net OD

```{r}
percBindingTableDiv()
```


```{r}
if(doc.type != "HTML"){
  view_plate(
    assayPlate_percBinding() %>% mutate(percBinding = round(percBinding, 2)),
    well_ids_column = "wells",
    columns_to_display = c("percBinding")
  )[[1]]
}
```


# Standard Curve

## Curve type: `r modelType` 

The included standards were: 

```{r}
standards_included()
```

The net OD values with means and CVs for standards were:

```{r}
assayPlate_indPlusMean_netOD() %>%
  filter(type == "STD")
```


```{r}
stdCurvePlot()
```

The coefficients for the model are

```{r}
stdCurve()$coefficients
```

# Calculations

Using the curve we calculated above, we can now estimate the amount of corticosterone that was in each well.
From the pg/well, we can calculate the concentration (in pg/mL) of the sample + assay buffer dilution if we know the volume added to the well: *pg/well \* volPerWell*
From the pg/mL concentration, we can convert to ng/mL: *pg/mL / 1000*
Finally, using the dilution factor of the original serum sample in the assay buffer, we can calculate the corticosterone concentration of the original serum sample: *ng/mL \* dilutionFactor*

```{r}
calcPlateDiv()
```

## On STD curve
```{r}
samplesOnStdCurvePlot()
```

### Quality control
```{r}
stdCurvePlot() +
  geom_point(data = samplesEst() %>% filter(type == "QC"), size = 2.5)
```

`r if(doc.type == "HTML") "## Table"`

```{r}
comboPlate()
```


```{r}
if(doc.type == "HTML"){
  assayPlate_concEstimates_meanCV() %>%
      relocate(
        netOD,
        .after = time
      ) %>%
    mutate(
      across(
        c(
          "cortMean",
          "cortCV",
          "percBinding",
          "pgPerWell",
          "pgPer_mL",
          "ngPer_mL",
          "sampleConc_ngPer_mL"
        ),
        ~ round(.x, 3)
      )
    )
}
```




